Reliable analytic approximation of pseudo-$\cl$ covariances

### 2019-05-18 draft/paper.tex
added paragraph about corr diff

>>>>

The goodness of the approximation is also seen in the correlation matrices.
The subtraction of the correlation matrix from the simulations and that from
the best analytical approximation (which we have just seen gives almost same
results as the spin-0 one) shows no structure but for the case of the larger
scales of the EEEE modes (see Fig.~\ref{fig:TTTT_EEEE_corr}).

\begin{figure*} %[htb]
  \centering
  \includegraphics[width=\columnwidth]{./figures/run_sph_Efstathiou_TTTT_correlation_difference.png}~
  \includegraphics[width=\columnwidth]{./figures/run_sph_Efstathiou_EEEE_correlation_difference.png}
  \caption{Differences between the simulations and analytical approximation of
    the correlation matrices for the TTTT (left) and EEEE (right) cases.}
  \label{fig:TTTT_EEEE_chi2}
\end{figure*}
